Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-28 latex/coverletter.tex
Update coverletter

It is our pleasure to submit this manuscript entitled \textit{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction} (authored by Roger A. Braker Yufan Luo, Lucy Y. Pao and Sean Andersson) for consideration to be published in the Transactions on Mechatronics. This paper is submitted for possible publication in the Focused Section on Nano/Micro 
Motion  Systems:  Design,  Sensing  and  Control(NMMS).

While sub-sampling schemes have seen increased attention recently, many of the existing studies are based purely on simulation. In contrast, this manuscript largely focuses on the experimental challenges which must be overcome to realize a sub-sampling scheme.

@@

\par\bigskip
\noindent Sincerely,
\par\bigskip
\noindent R.A. Braker\par
\noindent Y. Luo\par
\noindent L.Y. Pao
\noindent S. Andersson

>>>>

It is our pleasure to submit this manuscript entitled \textit{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction} (authored by Roger A. Braker, Yufan Luo, Lucy Y. Pao and Sean Andersson) for consideration to be published in the Transactions on Mechatronics. This paper is submitted for possible publication in the Focused Section on Nano/Micro Motion  Systems:  Design,  Sensing  and  Control(NMMS).

The main goal of this manuscript is to show that the native imaging speed of an atomic force microscope (AFM) can be improved by under-sampling  the specimen (i.e., only acquiring a subset of the total pixels for a target image size). While sub-sampling schemes have seen increased attention recently, many of the existing studies are based purely on simulation. However, the AFM is fundamentally a mechanical device and most of these sub-sampling studies provide little insight
into how the instrument will respond to the proposed sampling patterns nor into how the patterns might be implemented. Our manuscript seeks to partially fill this gap, as it largely focuses on the practical challenges which must be overcome to realize a sub-sampling scheme.

@@

\par\bigskip
\noindent Sincerely,
\par\bigskip
\noindent R.A. Braker\par
\noindent Y. Luo\par
\noindent L.Y. Pao\par
\noindent S. Andersson
